### 2008-12-15 doc/sec/SecurityFrameworkofARC1.tex
Description for slcs configuration into Security techinical document

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ The SLCS service is also a Web Service (standard Web Service
implemented by using ARC service interface), and the SLCS client is a
specific command-line interface (CLI) which includes the user agent and
WS client. The whole process of SLCS invocation is showed in Figure 7
(from step 1 to step 8), which is the same as in Figure 6, except that
step 7 and step 8 are invoked for the SLCS certificate request and
response.}

@@

>>>>

{\selectlanguage{english}\color{black}
\ \ \ \ The SLCS service is also a Web Service (standard Web Service
implemented by using ARC service interface), and the SLCS client is a
specific command-line interface (CLI) which includes the user agent and
WS client. The whole process of SLCS invocation is showed in Figure 7
(from step 1 to step 8), which is the same as in Figure 6, except that
step 7 and step 8 are invoked for the SLCS certificate request and
response.}

@@

{\selectlanguage{english}\color{black}
\ \ \ \ SLCS service is supposed to run together with SP service for
achieving the SAML2 SSO profile. A typical configuration for SLCS
service is as follows:}

\begin{center}
\tablehead{}\begin{supertabular}{|m{5.6886597in}|}
\hline
{\selectlanguage{english}\itshape\color{black}
\ \ \ \ {\textless}/Chain{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}tcp.service{\textquotedbl}
id={\textquotedbl}tcp{\textquotedbl}{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}tls{\textquotedbl}/{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tcp:Listen{\textgreater}{\textless}tcp:Port{\textgreater}60000{\textless}/tcp:Port{\textgreater}{\textless}/tcp:Listen{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}/Component{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}tls.service{\textquotedbl}
id={\textquotedbl}tls{\textquotedbl}{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}http{\textquotedbl}/{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:KeyPath{\textgreater}./testkey-nopass.pem{\textless}/tls:KeyPath{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:CertificatePath{\textgreater}./testcert.pem{\textless}/tls:CertificatePath{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}!-{}-tls:CACertificatePath{\textgreater}./cacert.pem{\textless}/tls:CACertificatePath-{}-{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:ClientAuthn{\textgreater}false{\textless}/tls:ClientAuthn{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}/Component{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}http.service{\textquotedbl}
id={\textquotedbl}http{\textquotedbl}{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}plexer{\textquotedbl}{\textgreater}POST{\textless}/next{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}/Component{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}Plexer
name={\textquotedbl}plexer.service{\textquotedbl}
id={\textquotedbl}plexer{\textquotedbl}{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}samlsp{\textquotedbl}{\textgreater}/saml2sp{\textless}/next{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}soap{\textquotedbl}{\textgreater}/slcs{\textless}/next{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}/Plexer{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}soap.service{\textquotedbl}
id={\textquotedbl}soap{\textquotedbl}{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}slcs{\textquotedbl}/{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}SecHandler
name={\textquotedbl}saml2ssoserviceprovider.handler{\textquotedbl}
id={\textquotedbl}saml2ssosp{\textquotedbl}
event={\textquotedbl}incoming{\textquotedbl}/{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}/Component{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}Service
name={\textquotesingle}saml.sp{\textquotesingle}
id={\textquotesingle}samlsp{\textquotesingle}{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}MetaDataLocation{\textgreater}./test\_metadata.xml{\textless}/MetaDataLocation{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}ServiceProviderName{\textgreater}https://squark.uio.no/shibboleth-sp{\textless}/ServiceProviderName{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}/Service{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}Service
name={\textquotedbl}slcs.service{\textquotedbl}
id={\textquotedbl}slcs{\textquotedbl}{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}slcs{\textquotedbl}/{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}slcs:CACertificate{\textgreater}./CAcert.pem{\textless}/slcs:CACertificate{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}slcs:CAKey{\textgreater}./CAkey.pem{\textless}/slcs:CAKey{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}slcs:CASerial{\textgreater}./CAserial{\textless}/slcs:CASerial{\textgreater}}

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ {\textless}/Service{\textgreater}}

\selectlanguage{english}\itshape\color{black}
\ \ \ \ {\textless}/Chain{\textgreater}\\\hline
\end{supertabular}
\end{center}
{\selectlanguage{english}\color{black}
\ \ \ \ As shown in the above table, a plexer dispatches the message
flow (outgoing from \textit{http.service}) into two SP service
(\textit{saml.sp}) and SOAP service (\textit{soap.service}). Since the
client authentication is switched off, it is not necessary to configure
{\textless}\textit{CACertificatePath}{\textgreater} or
{\textless}\textit{CACertificateDir}{\textgreater} for TLS MCC.}

{\selectlanguage{english}\color{black}
\ \ \ \ SP service needs to be configured with
{\textless}\textit{MetaDataLocation}{\textgreater} and
{\textless}\textit{ServiceProviderName}{\textgreater}. }

{\selectlanguage{english}\color{black}
\ \ \ \ SLCS service needs to be configured with
{\textless}\textit{CACertificate}{\textgreater}
{\textless}\textit{CAKey}{\textgreater} and
{\textless}\textit{Caserial}{\textgreater}.}
